\begin{enumerate}
%\item \textit{•}\\ \textit{•} \textbf{•}

\item \textit{Size Matters: From Two Dimensional Au(I)-Tl(I) Metallopolymers to Molecular Complexes}\\
T. Seifert, N. Knoefel, T. Feuerstein, K. Reiter, S. Lebedkin, M. Gamer, A. Boukis, F. Weigend, M. Kappes, P. Roesky, in Vorbereitung (2018).

\item \textit{[Co@Sn$_6$Sb$_6$]$^{3-}$: Structure and $^{119}$Sn NMR Spectrum of an Off-Center Endohedral 12-Vertex Cluster}\\
R. J. Wilson, F. Hastreiter, K. Reiter, P. Büschelberger, R. Wolf, R. Gschwind, F. Weigend, S. Dehnen, eingereicht (2018).

\item \textit{[Hg$_4$Te$_8$(Te$_2$)$_4$]$^{8-}$: A Heavy Metal Porphyrinoid Embedded in a Lamellar Structure}\\
C. Donsbach, K. Reiter, D. Sundholm, F. Weigend, S. Dehnen, \textit{Angew. Chem. Int. Ed.} \textbf{57}, 8770, (2018).

\item \textit{Multicomponent Reactions Provide Key Molecules for Secret Communication}\\ 
A. Boukis, K. Reiter, M. Frölich, D. Hofheinz, M. Meier, \textit{Nat. Commun.} \textbf{9}, 1439 (2018).

\item \textit{(Ge$_2$P$_2$)$^{2-}$: A Binary Analogue of P$_4$ as a Precursor to the Ternary Cluster Anion [Cd$_3$(Ge$_3$P)$_3$]$^{3-}$}\\
S. Mitzinger, J. Bandemehr, K. Reiter, J. McIndoe, X. Xie, F. Weigend, J. Corrigan, S. Dehnen, \textit{Chem. Commun.} \textbf{54}, 1421 (2018).

\item \textit{Calculation of Magnetic Shielding Constants with meta-GGA Functionals Employing the Multipole-Accelerated Resolution of the Identity: Implementation and Assessment of Accuracy and Efficiency}\\ 
K. Reiter, F. Mack, F. Weigend, \textit{J. Chem. Theory Comput.} \textbf{14}, 191 (2018).

\item \textit{An NHC-Phosphinidenyl as a Synthon for New Group 13/15 Compounds}\\
O. Lemp, M. Balmer, K. Reiter, F. Weigend, C. von Hänisch, \textit{Chem. Commun.} \textbf{53}, 7620 (2017).

\item \textit{Vibrational Circular Dichroism Spectra for Large Molecules and Molecules with Heavy Elements}\\
K. Reiter, M. Kühn, F. Weigend, \textit{J. Chem. Phys.} \textbf{146}, 054102 (2017).

\item \textit{A Dinuclear Gold(I) Bis(Carbene) Complex Based on a Ditopic Cyclic (Aryl)\\(Amino)Carbene Framework}\\
E. Deck, K. Reiter, W. Klopper, F. Breher, \textit{Z. Anorg. Allg. Chem.} \textbf{642}, 1320 (2016).

\item \textit{A Boron-Fluorinated Tris(pyrazolyl)borate Ligand ($^FTp^*$) and Its Mono- and Dinuclear Copper Complexes [Cu($^FTp^*$)$_2$] and [Cu$_2$($^FTp^*$)$_2$]: Synthesis, Structures, and DFT Calculations}\\
T. Augenstein, F. Dorner, K. Reiter, H. Wagner, D. Garnier, W. Klopper, F. Breher, \textit{Chem. Eur. J.} \textbf{22}, 7935 (2016).

\item \textit{[(Pb$_6$I$_8$)\{Mn(CO)$_5$\}$_6$]$^{2-}$: An Octahedral (M$_6$X$_8$)-like Cluster with Inverted Bonding}\\
S. Wolf, K. Reiter, F. Weigend, W. Klopper, C. Feldmann, \textit{Inorg. Chem.} \textbf{54}, 3989 (2015).
\end{enumerate}